On the presentation of orthogonal groups over polynomial rings

### 2019-05-17 dl-paper.tex
Many minor fixes

In our computations we will use two explicit elements of $\K_2(\Phi, R)$. Recall that Steinberg symbols are defined for any $s, t \in R^*$ by the identity
\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \]

@@

\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
\begin{proof} The result follows from consideration of the commutative diagram
\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by the above lemma. \end{proof}
\begin{theorem} \label{thm41}
Assume the notation of~\cref{lem:lemma32} and suppose additionally that $2$ is invertible in $A$.
Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
\end{theorem}
\begin{proof}
 Consider the following commutative diagram with exact rows, in which the lifting $t$ is obtained from~\cref{lem:lemma32}:
\begin{equation*} \xymatrix{
 C(\rD_\ell, B, I) \ar[r]^{j_B} \ar@{->>}[d]_{f} & \St(\rD_\ell, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
 \St(\rD_\ell, B) \ar[r]^{\pi_B} \ar[d]_{h} & \St(\rD_\ell, k[X]) \ar[d]_{i} \\
 C(\rD_\ell, R, I) \ar[r]^{j_R}         & \St(\rD_\ell, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
 \St(\rD_\ell, R) \ar[r]^-{\pi_R}        & \St(\rD_\ell, k[X, X^{-1}]).
}\end{equation*}
Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$
 also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\rD_\ell, B, I)$ via $\mu_B$.
Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $j_R(c) = g(b)$. 
By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$ and we obtain the required assertion:
 \[ 1 = \mu_Bj_B(d) = tgj_B(d) = tj_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]

\end{proof}

@@

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map induced by the embedding $A[X] \subseteq A[X, X^{-1}]$:
\begin{enumerate}
 \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, \xi),\ \alpha \perp \beta;$
 \item $x_{-\alpha}(X^2f);$
 \item $x_{\alpha}(f);$
 \item Dennis--Stein symbols $\langle a, m \rangle$, $a\in A$, $m\in M$.
\end{enumerate}
In the above formulae and for the rest of this subsection we assume $f \in M[X]$ and $\xi \in A[X]$.
\end{df}

Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(Xm)$, $m \in M$. The following lemma shows that this subgroup is sufficiently large.
\begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$. 
Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we obtain that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$. Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], XM[X])$.

Now choose $\gamma$ to be arbitrary root orthogonal to $\alpha$. By~\cref{Kgen-strong} we are left to prove that $c_{\pm \gamma}(f, X\xi)$ lies in $P_\alpha(*)$. 
But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of $P_\alpha(0)$ of type 3. \end{proof}

The above lemma allows us to give the following alternative characterization for the subgroup $P_\alpha(*)$:
 it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup generated by
 elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
 and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}.

\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r]^{p_\alpha} & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
\begin{proof} 
We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
The assertion is obvious for the generators of type 3, 4 and 6.

@@

\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed as follows. Express $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta \perp \alpha$. Now $p_\alpha(g)$ coincides with the sum of constant terms of the polynomials $f$ corresponding to the factors of the form $z_{-\alpha}(Xf, \xi)$ occuring in this expression. \end{rem}

For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
From the above lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.

@@

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for generators of type 3, 5 and 6.
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
Clearly, the expression in the right hand side is a product of generators of type 5, 2, 1.

@@

\begin{lemma} \label{lem:Tulenbayev-formula} 
One has 
$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose some $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
 \begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
 = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
\end{multline*}
which implies the assertion.
\end{proof}

@@

 It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$. The reverse inclusion follows from the just proved decomposition and the fact that for $g\in K(A[X], M[X])$ by~\cref{rem:palpha} one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$. \end{proof}

 We need one more technical definition.
 \begin{df} Denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
 \end{df}

\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$.
\end{lemma}
\begin{proof} 
To simplify notation we call the generators of the subgroup $Z$ ``generators of type 6``, despite the fact that these elements are not always contained in $K(\alpha, \beta)$ (or even $K(A[X], M[X])$).

By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 6, 6, 1.
By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 6, 1, 2, 1, 1, 6, 6.
The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a products of generators of type 2, 1. As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 6, 6, 5. \end{proof}

\begin{corollary} The image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
\begin{proof} Follows from the above lemma and the fact that the generators of $Z$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
 Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
  $\gamma = \alpha - \beta$, a contradiction. \end{proof}

\begin{lemma} \label{lem:SRsharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P_\beta\left(\tfrac{m'}{1 + am}\right). \] \end{lemma}
\begin{proof}
 By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that
 \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

@@

\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate to $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.

 Throughout this proof we understand generator types according to~\cref{defP0}.
 It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.

 In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{\gamma + \beta -\alpha} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi. \]
 Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = \langle \gamma , \alpha \rangle + \langle \beta, 
 \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, 
 therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2. {\bf TODO: } Double check that both possibilities actually occur.

Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
Since $\langle \beta - \gamma - \alpha , \alpha \rangle = \langle \beta , \alpha \rangle - \langle \gamma , \alpha \rangle - \langle \alpha, \alpha \rangle \leq 1 - 1 - 2 = -2$
we obtain that $\beta - \gamma - \alpha = -\alpha$. Thus, by \eqref{Z3} of~\cref{Zrels}
\[z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\gamma,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\gamma}(f, X\xi). \]
The expression in the right-hand side is a product of generators of type 1, 4, 2. \end{proof}

>>>>

In our computations we will use two explicit elements of $\K_2(\Phi, R)$. Recall that Steinberg symbols are defined for any $s, t \in R^*$ by the identity
\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \end{equation}

@@

\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
\begin{proof} The result follows from consideration of the commutative diagram
\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by the above lemma. \end{proof}
\begin{theorem} \label{thm41}
Assume the notation of~\cref{lem:lemma32} and suppose additionally that $2$ is invertible in $A$.
Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
\end{theorem}
\begin{proof}
 Consider the following commutative diagram with exact rows, in which the lifting $t$ is obtained from~\cref{lem:lemma32}:
\begin{equation*} \xymatrix{
 C(\rD_\ell, B, I) \ar[r]^{j_B} \ar@{->>}[d]_{f} & \St(\rD_\ell, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
 \St(\rD_\ell, B) \ar[r]^{\pi_B} \ar[d]_{h} & \St(\rD_\ell, k[X]) \ar[d]_{i} \\
 C(\rD_\ell, R, I) \ar[r]^{j_R}         & \St(\rD_\ell, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
 \St(\rD_\ell, R) \ar[r]^-{\pi_R}        & \St(\rD_\ell, k[X, X^{-1}]).
}\end{equation*}
Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$
 also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\rD_\ell, B, I)$ via $\mu_B$.
Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $j_R(c) = g(b)$. 
By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$ and we obtain the required assertion:
 \[ 1 = \mu_Bj_B(d) = tgj_B(d) = tj_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
\end{proof}

@@

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map induced by the embedding $A[X] \subseteq A[X, X^{-1}]$:
\begin{enumerate}
 \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, \xi),\ \beta \in Z_0(\alpha);$
 \item $x_{-\alpha}(X^2f);$
 \item $x_{\alpha}(f)$.
\end{enumerate}
In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. \end{df}

\begin{rem}\label{rem:c-DS}
From our assumptions on $\Phi$ it follows that $Z_0(\alpha)$ is nonempty, hence $P_\alpha(0)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ ($a\in A$, $m\in M$) and elements $c_{\pm \gamma}(f, X\xi)$ for $\gamma \in Z_0(\alpha)$ (both can be expressed as products of generators of type 3).
\end{rem}

Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(Xm)$, $m \in M$. The following lemma shows that the resulting subgroup is sufficiently large.
\begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $\St(\Phi, A[X], XM[X])$. The required assertion now follows from~\cref{Kgen-strong} and the preceding remark. \end{proof}

The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup generated by
 elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
 and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}.

\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r]^{p_\alpha} & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
\begin{proof} 
We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
The assertion is obvious for the generators of type 3 and 4.

@@

\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed via the following procedure. Start with any presentation of $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta\in Z_0(\alpha)$. Now pick among these factors those that correspond to the root $\beta = -\alpha$ (i.\,e. pick all factors $z_{-\alpha}(Xf_i, \xi_i)$). Now $p_\alpha(g)$ is precisely the sum of constant terms of the polynomials $f_i$. \end{rem}

For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
From the preceding lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.

@@

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for generators of type 3 and 5.
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
Clearly, the expression in the right hand side is a product of generators of type 5, 2, 1.

@@

\begin{lemma} \label{lem:Tulenbayev-formula} 
One has 
$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation using~\eqref{eq:conj-h-x},\eqref{eq:conj-h-h},\eqref{eq:steinberg},\eqref{eq:dennis-stein} shows that
 \begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
\end{multline*}
which implies the assertion.
\end{proof}

@@

 It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$. The reverse inclusion follows from the just proved decomposition and the fact that for $g\in K(A[X], M[X])$ one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}). \end{proof}

 We need one more technical definition.
 \begin{df} Denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.\end{df}

\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$. \end{lemma}
\begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``. By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type Z, Z, 1.
By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z.
The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a products of generators of type 2, 1. As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type Z, Z, 5. \end{proof}

\begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
\begin{proof} Follows from the above lemma and the fact that the generators of $Z_{\alpha,\beta}$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
 Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
  $\gamma = \alpha - \beta$, a contradiction. \end{proof}

\begin{lemma} \label{lem:SRsharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P_\beta\left(\tfrac{m'}{1 + am}\right). \] \end{lemma}
\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

@@

\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate to $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. Throughout the proof we understand generator types according to~\cref{defP0}. It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.

 In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{-\alpha + \gamma + \beta} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi. \] Notice that $\langle \alpha - \beta - \gamma, \alpha \rangle = \langle \alpha, \alpha \rangle - \langle \beta, \alpha \rangle - \langle \gamma, \alpha \rangle \leq 2 - 1 - 1 = 0$, 
 hence $\langle \alpha - \beta - \gamma, \alpha \rangle = -1,0$ and the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2.

Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
Since $\langle \alpha - \beta + \gamma, \alpha \rangle = \langle \alpha , \alpha \rangle - \langle \beta, \alpha \rangle + \langle \gamma, \alpha \rangle \geq 2 - 1 + 1 = 2$
we obtain that $\alpha - \beta + \gamma = \alpha$. Thus, by \eqref{Z3} of~\cref{Zrels}
\[z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\gamma,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\gamma}(f, X\xi). \]
The expression in the right-hand side is a product of generators of type 1, 4, 2. \end{proof}
